Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-07-08 ms/Thesis/thesis.tex
Move the description of the invasion model and the population str. model to the model section

Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}a). 
Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is 
\begin{equation} \label{eq:vertical_oblique_transmission}
P(\phi'=A \mid \phi) = \begin{cases}
v + (1-v)p, & \text{if } \phi=A \\
(1-v)p, & \text{if } \phi=B
\end{cases},
\end{equation}
where $p=P(\phi=A)$ is the frequency of $A$ among all adults in the parental generation.

@@

%%% Figure: model illustration
\begin{figure}[pt]
  \centering
  \includegraphics[width=0.7\textwidth]{../PRSB_figures/fig_1.pdf}
  \caption{\textbf{Model illustration.} 
  \textbf{(a)}~First, offspring inherit their parent's phenotype via vertical cultural transmission with probability $v$, or the phenotype of a random non-parental adult via oblique cultural transmission with probability $1-v$.
  \textbf{(b)}~Second, adults socially interact in pairs in a prisoner's dilemma game. Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
  \textbf{(c)}~The prisoner's dilemma payoff matrix shows the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
    \textbf{(d)}~The probabilities of successful horizontal cultural transmission of phenotypes $A$ (cooperator) and $B$ (defector) are $T_A$ and $T_B$, respectively.
    }
  \label{fig:illustration}
\end{figure}

@@

@@

\begin{figure}[p]
  \centering       
    \includegraphics[width=1\textwidth]{../PRSB_figures/fig_2.pdf}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
	In all cases the vertical transmission rate $v$ is on the x-axis.
	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (Eqs.~\ref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively. 
    (\textbf{c-d})~Interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively. 
    Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
    Here, $T_A = 0.5$, and
    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
    }
    \label{fig:equilibria}
\end{figure}

@@

\begin{figure}[p]
  \centering       
	\includegraphics[width=1\textwidth]{../PRSB_figures/fig_3.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
    (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
    In panels \textbf{(a)} and \textbf{(b)}, the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
	In panel \textbf{(c)}, interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
    Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
    \textbf{(d)}~Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$). % todo ref eq 12
    The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
    Black circles show the three equilibria.
  	}
    \label{fig:equilibria_v1}
\end{figure}
\newpage

@@

\begin{figure}[h]
  \centering       
    \includegraphics[scale=0.5]{../Figures/Unstable_Time_series.eps}
    \includegraphics[scale=0.5]{../Figures/Stable_Time_series.eps}
    \caption{\textbf{Stable and unstable equilibrium dynamics} 
    The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
    In \textbf{(a)} the system has unstable equilibrium and therefore, all the curves are moving away from it.
    In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b)} $T_B=0.7$, $\alpha=0.6$ and $b=2.3$.}
    \label{fig:time_series}
\end{figure}

@@

%%% Figure: Invasion
\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_s1.pdf}
  \caption{
  \textbf{Reduction principle for interaction-transmission association.} 
  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (Eq.~D1).
  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
  Here, $v=1$, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
  }
  \label{fig:invasion}
\end{figure}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Population structure}
All the simulations in this section were made by Ohad Lewin-Epstein from Tel Aviv University.
Interaction-transmission association may also emerge from population structure.
Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
initiators interact with a random neighbor (i.e. individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}c) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.
The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in neighbourhoods close to the grid border.
As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.

The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
Changing the simulation so that selection is local (i.e. sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).

@@

%%% Figure: Spatial model - global selection
\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_4.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~\textbf{(a)}, or the transmission bias, $T_A-T_B$, on the x-axis of panel~\textbf{(b)}.
  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
	The inset in panel~\textbf{(b)} focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
	This stochastic polymorphism is illustrated in panel~\textbf{(c)}, which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~\textbf{(b)}.
  In all cases, the population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between neighbouring sites, and each site has 8 neighbours.
  Selection operates globally (see Figure S2 for results from a model with local selection).
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
  \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
  }
  \label{fig:spatial}
\end{figure}

@@

%%% Figure: Spatial model - local selection
\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_s2.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population with local selection.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
  Cooperation and horizontal transmission are both local between neighbouring sites, and each site had 8 neighbours.
  Selection operates locally (see Figure 4 for results from a model with global selection).
  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~14 for panel~\textbf{(a)} and in Eqs.~12 for panel~\textbf{(b)}.
  The population evolves on a 100-by-100 grid.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
  50 simulations were executed for each parameter set.
  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
  }
  \label{fig:spatial_local_selection}
\end{figure}

>>>>

\subsection{Basic Model}
\label{section:basicmodel}
Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}a). 
Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is 
\begin{equation} \label{eq:vertical_oblique_transmission}
P(\phi'=A \mid \phi) = \begin{cases}
v + (1-v)p, & \text{if } \phi=A \\
(1-v)p, & \text{if } \phi=B
\end{cases},
\end{equation}
where $p=P(\phi=A)$ is the frequency of $A$ among all adults in the parental generation.

@@

%%% Figure: model illustration - basic model
\begin{figure}[pt]
  \centering
  \includegraphics[width=0.7\textwidth]{../PRSB_figures/fig_1.pdf}
  \caption{\textbf{Model illustration.} 
  \textbf{(a)}~First, offspring inherit their parent's phenotype via vertical cultural transmission with probability $v$, or the phenotype of a random non-parental adult via oblique cultural transmission with probability $1-v$.
  \textbf{(b)}~Second, adults socially interact in pairs in a prisoner's dilemma game. Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
  \textbf{(c)}~The prisoner's dilemma payoff matrix shows the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
    \textbf{(d)}~The probabilities of successful horizontal cultural transmission of phenotypes $A$ (cooperator) and $B$ (defector) are $T_A$ and $T_B$, respectively.
    }
  \label{fig:illustration}
\end{figure}

@@

\subsection{Invasion Model}
In this section, we use the model described in \autoref{section:basicmodel}. 
Here we assume a coexistence of both phenotypes (cooperators and defectors) and that the frequency of each phenotye stays the same each generation.
Henece, we assume that the we start from one of the equilibrium.
In addition, we assume that the equilibria is stable.  Denote the frequency of cooperators in the population in $\hat{p}^*$ and frequency of defectors $1-\hat{p}^*$.

Starting from the assumption described above we want to investigate the evolution of interaction-transmission association $\alpha$.
We assume that the initial population has interaction-transmission association $\alpha_1$. 
We want to answer the question what would happen to cooperators frequency if a new mutation would occur and change the interaction-transmission association to a different value $\alpha_2$ without direct effect on fitness.
We can think of this model as an invasion model where the invadors are the individuals with interaction-transmission association $\alpha_2$. \autoref{fig:invasion_illustration} illustrates the invasion.

%%% Figure: model illustration - invasion model
\begin{figure}[pt]
  \centering
  \includegraphics[width=0.7\textwidth]{../PRSB_figures/fig_2.pdf}
  \caption{\textbf{Invasion model illustration.} Starting from stable equilibrium with coexistence of both phenotypes. 
  A mutation that has effect only the interaction-transmission association tries to invade. }
  \label{fig:invasion_illustration}
\end{figure}

\newpage
\subsection{Population structure model}
\label{sec:spatialModel}
Interaction-transmission association may also emerge from population structure.
Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
initiators interact with a random neighbor (i.e. individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}c) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.
The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in neighbourhoods close to the grid border.
As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.

@@

\begin{figure}[p]
  \centering       
    \includegraphics[width=1\textwidth]{../PRSB_figures/fig_3.pdf}
    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
	In all cases the vertical transmission rate $v$ is on the x-axis.
	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (Eqs.~\ref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively. 
    (\textbf{c-d})~Interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively. 
    Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
    Here, $T_A = 0.5$, and
    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
    }
    \label{fig:equilibria}
\end{figure}

@@

\begin{figure}[p]
  \centering       
	\includegraphics[width=1\textwidth]{../PRSB_figures/fig_4.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
    (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
    In panels \textbf{(a)} and \textbf{(b)}, the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
	In panel \textbf{(c)}, interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
    Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
    \textbf{(d)}~Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$). % todo ref eq 12
    The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
    Black circles show the three equilibria.
  	}
    \label{fig:equilibria_v1}
\end{figure}
\newpage

@@

\begin{figure}[h]
  \centering       
    \includegraphics[scale=0.5]{../Figures/Unstable_Time_series.eps}
    \includegraphics[scale=0.5]{../Figures/Stable_Time_series.eps}
    \caption{\textbf{Unstable and stable equilibrium dynamics} 
    The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
    In \textbf{(a)} the system has unstable equilibrium and therefore, all the curves are moving away from it.
    In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b)} $T_B=0.7$, $\alpha=0.6$ and $b=2.3$.}
    \label{fig:time_series}
\end{figure}

@@

%%% Figure: Invasion
\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_6.pdf}
  \caption{
  \textbf{Reduction principle for interaction-transmission association.} 
  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (Eq.~D1).
  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
  Here, $v=1$, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
  }
  \label{fig:invasion}
\end{figure}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Population structure}
Here, we are going to run stochastic simulations to learn more about evolution of Cooperation when the population is structured. 
The model is described in \autoref{sec:spatialModel}.
All the simulations in this section were made by Ohad Lewin-Epstein from Tel Aviv University.
The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
Changing the simulation so that selection is local (i.e. sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).

@@

%%% Figure: Spatial model - global selection
\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_7.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~\textbf{(a)}, or the transmission bias, $T_A-T_B$, on the x-axis of panel~\textbf{(b)}.
  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
	The inset in panel~\textbf{(b)} focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
	This stochastic polymorphism is illustrated in panel~\textbf{(c)}, which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~\textbf{(b)}.
  In all cases, the population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between neighbouring sites, and each site has 8 neighbours.
  Selection operates globally (see Figure S2 for results from a model with local selection).
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
  \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
  }
  \label{fig:spatial}
\end{figure}

@@

%%% Figure: Spatial model - local selection
\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_8.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population with local selection.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
  Cooperation and horizontal transmission are both local between neighbouring sites, and each site had 8 neighbours.
  Selection operates locally (see Figure 4 for results from a model with global selection).
  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~14 for panel~\textbf{(a)} and in Eqs.~12 for panel~\textbf{(b)}.
  The population evolves on a 100-by-100 grid.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
  50 simulations were executed for each parameter set.
  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
  }
  \label{fig:spatial_local_selection}
\end{figure}
